River networks dampen long-term hydrological signals of climate change

### 2017-04-18 drafts/PNAS/Chezik_PNAS_SI.tex
Final Pre-Submission Edits

\section*{Supplementary Information}
The following supplementary material includes 4 additional figures. Figures \ref{fig:S1} and \ref{fig:S2} are similar to figure 4 in the main text where monthly trends in flow are shown for the basin along with trend attenuation results. These supplementary figures highlight minimum and median seasonal flow trends rather than maximum seasonal flow trends. Figures \ref{fig:S3} and \ref{fig:S4} are example plots demonstrating a single null-model iteration for the median flow metric.

>>>>

\section*{Supplementary Information}
The following supplementary material includes 4 additional figures. Figures \ref{fig:S1} and \ref{fig:S2} are similar to figure 4 in the main text where Fraser River basin monthly flow trends are shown along with trend attenuation results. These supplementary figures highlight minimum and median seasonal flow trends rather than maximum seasonal flow trends. Figures \ref{fig:S3} and \ref{fig:S4} are example plots demonstrating a single null-model iteration for the median flow metric.
